Estimating the magnetization distribution within rectangular rock samples

### 2016-07-25 manuscript/manuscript.tex
create the diff file

The inversion method proposed here is implemented in the Python programming
language.
Our implementation relies on the open-source library
numpy \citep[][ \url{http://scipy.org}]{jones2001, walt2011}
for array-based computations,
matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
for plots and maps,
and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
for implementing the forward problem.

The computational experiments
(e.g., data processing, synthetic tests, real data application)
were performed in
Jupyter (formerly IPython) notebooks
\citep[][ \url{http://jupyter.org/}]{perez2007}.
The notebook files combine the source code,
the results and figures generated by the code
and rich text to explain the analysis.

All source code, Jupyter notebooks, data, and results
can be found at the online repository
\url{https://github.com/pinga-lab/magnetization-rock-sample} 
(\textbf{Note to reviewers: the online repository will be made public upon
publication}).
An archived version of this repository is also available at
\url{http://dx.doi.org/...}
(\textbf{Note to reviewers: the archived version will be uploaded upon
publication}).

@@

\begin{acknowledgments}
We would like to thank E.L. Andrade, R. Trindade and V.C.F. Barbosa
for encouraging this work. We would also like to thank
IAG/USP Paleomagnetism and Rocks Magnetism laboratory for providing the
technical support to manufacture the synthetic sample.
The Figures and numerical computation were done in Python
by using the open-source library Fatiando a Terra 
(http://www.fatiando.org/index.html).
Reis was supported by a scholarship from Conselho Nacional 
de Desenvolvimento Cient\'{i}fico e Tecnol\'{o}gico (CNPq). 
Oliveira Jr. was supported by a grant (number 445752/2014-9)
from Conselho Nacional 
de Desenvolvimento Cient\'{i}fico e Tecnol\'{o}gico (CNPq).
\end{acknowledgments}

>>>>

The inversion method proposed here is implemented in the Python programming
language.
Our implementation relies on the open-source library
numpy \citep[][ \url{http://scipy.org}]{jones2001, walt2011}
%numpy \citep{jones2001, walt2011}
for array-based computations,
matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
%matplotlib \citep{hunter2007}
for plots and maps,
and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
%and Fatiando a Terra \citep{uieda2013}
for implementing the forward problem.

The computational experiments
(e.g., data processing, synthetic tests, real data application)
were performed in
Jupyter (formerly IPython) notebooks
\citep[][ \url{http://jupyter.org}]{perez2007}.
%\citep{perez2007}.
The notebook files combine the source code,
the results and figures generated by the code
and rich text to explain the analysis.

All source code, Jupyter notebooks, data, and results
can be found at the online repository
\url{https://github.com/pinga-lab/magnetization-rock-sample}.

@@

\begin{acknowledgments}
We would like to thank E.L. Andrade, R. Trindade and V.C.F. Barbosa
for encouraging this work. We would also like to thank
IAG/USP Paleomagnetism and Rocks Magnetism laboratory for providing the
technical support to manufacture the synthetic sample.
The Figures and numerical computation were done in Python
by using the open-source library Fatiando a Terra 
(\url{http://www.fatiando.org}).
Reis was supported by a scholarship from Conselho Nacional 
de Desenvolvimento Cient\'{i}fico e Tecnol\'{o}gico (CNPq). 
Oliveira Jr. was supported by a grant (number 445752/2014-9)
from Conselho Nacional 
de Desenvolvimento Cient\'{i}fico e Tecnol\'{o}gico (CNPq).
\end{acknowledgments}
